Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-21 2015-turklang-kazdep/paper.tex
some of table 1
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60958 72bbbca6-d526-0410-a7d9-f06f51895060

\begin{table}[htbp]
	\centering
	\caption{Primary syntactic functions of traditionally defined cases in Kazakh.}\label{tab:cases}
	\begin{small}
		\begin{tabular}{l p{5em} p{8em} p{22em}}
			\toprule
				\textbf{Case} & \textbf{Morpheme} & \textbf{Functions} & \textbf{Examples} \\
			\midrule
				nominative & - & subject\newline
										attributive\newline
										indefinite object\newline
										indefinite genitival 
									& hargle bargle \newline
										jargal barble \newline 
										\\
				accusative & -/NI/ & definite object\newline
											embedded subject\newline
											causative subject
										& foo \newline
											bar \\
				genitive & -/NIң/ & definite genitival\newline
											embedded subject \\
				locative & -/DA/ & adverbial
										& \\
				ablative & -/DAн/ & adverbial,\newline
											comparator \\
				dative & -/GA/ & indirect object,\newline
										attributive
									& \\
			\bottomrule
		\end{tabular}
	\end{small}
\end{table}

>>>>

\begin{table}[htbp]
	\centering
	\caption{Primary syntactic functions of traditionally defined cases in Kazakh.}\label{tab:cases}
	\begin{small}
		\begin{tabular}{l l p{8em} p{27.15em}}
			\toprule
				\textbf{Case} & \textbf{Morpheme} & \textbf{Functions} & \textbf{Examples} \\
			\midrule
				nominative & - & subject\newline
										attributive\newline
										indefinite object\newline
										indefinite genitival 
									& \kazakh{\textbf{Дәрігер} үйді көреді.} \gloss{\textbf{The doctor} sees the house.} \newline
										\kazakh{\textbf{қонақ} үй} \gloss{hotel (lit., \textbf{guest} house)} \newline 
										\kazakh{Дәрігер \textbf{үй} көреді.} \gloss{The doctor sees \textbf{a house}.}\newline
										\kazakh{\textbf{үй} жануарлары} \gloss{\textbf{house} animals} \\\midrule
				accusative & -/NI/ & definite object\newline
											embedded subject\newline
											intr.\ causative subj.
										& \kazakh{Дәрігер \textbf{үйді} көреді.} \gloss{The doctor sees \textbf{the house}.} \newline
											bar \\\midrule
				genitive & -/NIң/ & definite genitival\newline
											embedded subject
										& \kazakh{\textbf{үйдің} жануарлары} \gloss{the animals of \textbf{the house}} \newline
											\kazakh{Ол \textbf{Айгүлдің} ойнағанына қарап тұр.} \gloss{She's watching \textbf{Aygül} play.} \\\midrule
				locative & -/DA/ & adverbial
										& \\\midrule
				ablative & -/DAн/ & adverbial,\newline
											comparator \\\midrule
				dative & -/GA/ & indirect object\newline
										attributive\newline
										tr.\ causative subj.
									& \\\midrule
				instrumental & -/Mен/ &  \\
			\bottomrule
		\end{tabular}
	\end{small}
\end{table}
